quicR

### 2024-08-25 README.qmd
\n lol

subgraph A[Select the following export options]
  direction LR
  micro(Microplate View)
  table(Table View)
  trans(Transpose Table)
  test(Add test run \n information)
end

>>>>

subgraph A[Select the following export options]
  direction LR

  micro(Microplate View)
  table(Table View)
  trans(Transpose Table)
  test(Add test run \n information)
end
